Methods for Large Scale Learning to Rank

### 2014-03-11 report/Chapters/RelatedWork.tex
derde relevante backward search resultaat verwerkt

\subsection{GPGPU for Learning-to-Rank}
De Sousa et al. \cite{DeSousa2012} proposed a \ac{GPGPU} approach using the \ac{GPU} both learning the ranking function and for query processing, thereby improving both training time and query time. An association rule based Learning-to-Rank approach proposed by Veloso et al. \cite{Veloso2008} has been implemented using the \ac{GPU} in such a way that the set of rules van be computed in parallel, in different threads, for each document. A speed-up of 127X in query processing time is reported based on evaluation on the LETOR dataset. The speed-up achieved at learning the ranking function was unfortunately not stated.\\

>>>>

\subsection{GPGPU for Learning-to-Rank}
Wang et al. \cite{Wang2009} experimented with a \ac{GPGPU} approach for parallelising RankBoost. Nvida \ac{CUDA} and ATI Stream are the two main \ac{GPGPU} computing platform and are released by the two main \ac{GPU} vendors Nvidia and AMD. Experiments show a 22.9x speed-up on Nvida \ac{CUDA} and a 9.2x speed-up on ATI Stream.\\

De Sousa et al. \cite{DeSousa2012} proposed a \ac{GPGPU} approach to improve both training time and query evaluation through \ac{GPU} use. An association rule based Learning-to-Rank approach proposed by Veloso et al. \cite{Veloso2008} has been implemented using the \ac{GPU} in such a way that the set of rules van be computed in parallel, in different threads, for each document. A speed-up of 127X in query processing time is reported based on evaluation on the LETOR dataset. The speed-up achieved at learning the ranking function was unfortunately not stated.\\
